---
title: "FAHA -- Assignment 04"
date: 'Word count: 477'
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(tibble)
library(knitr)
```

<!-- Instructions -->
<!-- As always, please work to keep your responses succinct but understandable. This is a challenging assignment, but your answer should be no more than 500 words. Peer-reviewers have the authority to award zero points to a submission that exceeds the word limit. -->

<!-- This assignment aims to bring together several themes that have come up in the course thus far. Feel free to be creative, and do not feel bounded by reality in the datasets, methods or tools that are available to you. -->

<!-- (1) Present a research question. This should be in a qualitative form, something that could be communicated to someone without talking about datasets or methods. -->

<!-- (2) Reframe that research question into a question about patterns – i.e., ask a new version of the research question in (1), now drawing attention to the way(s) in which it might "secretly" be a question about patterns. -->

<!-- (3) Suggest a quantitative operationalization of those patterns on a particular data set. Define both the dataset and the type of answer your operationalization will deliver. You are welcome to invoke a fantasy dataset; it doesn't need to exist. You are likewise permitted a fantasy computational (machine learning) tool that can find patterns, but you should describe clearly what that tool will output. -->

<!-- (4) The payoff: how do you connect the "cold" quantiative pattern results of (3) to the "hot" questions of human experience in (1)? Again, feel free to imagine infinitely powerful algorithms that can find interesting patterns. -->

<!-- Grading rubric -->

<!-- Part (1): +3 -->
<!-- Part (2): +2 -->
<!-- Part (3) dataset: +2 -->
<!-- Part (3) operationalizaiton output: +2 -->
<!-- Part (4): +2 -->
<!-- Overall integration: +2 -->
<!-- Discretionary: +2 -->
<!-- Total: X of 15 points -->

# (1) Qualitative research question   

*"How do Twitter accounts influence each other regarding issues to talk about?"*  

**Definition:** *Issue* is public problem publicly recognized as publicly important.


# (2) Research question about patterns   

*"How do Twitter accounts of politicians, media and regular users influence each other in writing tweets about same issue?"*


# (3) Dataset and operationalization

## (3.1) *Dream* dataset  

We use tweets posted on Twitter in year 2020. We identify tweets mentioning some issue and sort these tweets according the main issue. We also sort the tweeting accounts into categories: *politician*, *medium*, *user*. For ***each tweet*** we record: authoring account, category of account, time of tweeting, main issue (or '*no issue*'), main issue of ***the last tweet*** of ***each followed account***, names and categories of these accounts and times of tweeting of these tweets.
<!-- We acquire complete information about relevant content on Twitter preceding each tweet. -->

<!-- ### Variables useful for constructing patterns   -->

We then compute: how account *imitates* issues from other accounts, what *pressure* the followed accounts cast on the account in focus, how *unique* is the coverage of an account, and how successfully an account *persuades* its followers to cover the same issues. 
<!-- We can find for each tweet preceding tweets covering same issue.  -->
We compute how many times the account covers the same issue as each of the followed accounts -- i.e. *imitation*. Then we compute what percentage of these accounts mention the same issue -- i.e. *pressure*. We also compute for each account the percentages of covered issues over time and how much do these percentages differ from percentages of issues covered by followed accounts -- i.e. *uniqueness*. We compute how many times the following accounts also cover the same issue as the account in focus  -- i.e. *persuasiveness*.      


## (3.2) Operationalization and its output

<!-- ### Types of accounts: -->

We use *imitation*, *pressure*, *uniqueness* and *persuasiveness* for definition of types of accounts according following table: 
<!-- Accounts with low *imitation*, low *pressure*, high *uniqueness* and moderate or high *persuasiveness* are ***builders***. Accounts with high *imitation*, low *pressure*, moderate *uniqueness* and high *persuasiveness* are ***transmitters***. Accounts with high *imitation*, high *pressure*, low *uniqueness* and moderate or low *persuasiveness* are ***receivers***. Accounts with low *imitation*, low *pressure*, high *uniqueness* and low *persuasiveness* are ***outcasts***.   -->

```{r}
types = tibble(`Type of account` = c("Builders", "Transmitters", "Receivers", "Outcasts"), 
               Imitation =         c("low",      "high",         "high",      "low"),
               Pressure =          c("low",      "low",          "high",      "low"),
               Uniqueness =        c("high",     "moderate",     "low",       "high"),
               Persuasiveness = c("moderate/high", "high",       "moderate/low", "low"))

kable(types)
```



### Patterns of relations:

<!-- We also look at the correlation of the ***type*** of account with the ***category*** of account.  -->
We find how many ***builders*** are *politicians*, *media* and *users*, same for  ***transmitters***, ***receivers*** and ***outcasts***. We also look how many *media* are ***builders***, ***transmitters***, ***receivers*** and ***outcasts***, same for *politicians* and *users*.  


### Hypothetical result:

We find that few *media* and *politicians* accounts are ***builders***; majority of *media*, half of *politicians* and minority of *users* are ***transmitters***; minority of *media*, half of *politicians* and majority of *users* are ***receivers***; and very small fraction of *media*, *politicians* and *users* are ***outcasts***. 
 
 
# (4) Payoff  
  
Our hypothetical result means that few *media* and *politicians* accounts build public sphere around important issues, their interplay and dialogue sets tone of public debate, they build the agenda of public sphere. Their accent on certain issues is then transmitted via persuasive *media*, *politicians* and minority of regular *users* accounts to the majority of regular Twitter *users*, rest of *media* and *politicians*. The very small fraction of ***outcasts*** means that public sphere is synchronized and issues resonate through almost whole public.
