---
title: "FAHA -- Assignment 02"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Important things to remember when submitting your work for peer review: -->
<!-- All submissions must be uploaded before 22 Sep 2021 8am CEST -->


# Question 1: Understanding

<!-- QUESTION 1: UNDERSTANDING   You succeed in measuring the extent to which the words used in a book's blurb predict the gender of the book's author. Let’s tell a story! -->
<!-- In the 1940s, there were very few women writing monographs in a certain field. Blurbs on the back of women's books looked similar to those on men's books. -->
<!-- By the 1970s, however, blurbs began to treat men and women authors in the field quite differently. -->
<!-- By the 2000s, greater awareness of equitable treatment, and sensitivity to gendered language choices, led this effect to decline. -->
<!-- Draw (sketch on paper* or digitally) a "signal strength" graph, using the example for the Old Bailey as a template [Chapter 1; 15:10]. Your graph should show the change in blurbs' capacity to signal the book author's gender, as described above. The graph should include: (1) labeled x and y axes (with words, briefly describe what each axis means), (2) a graph element corresponding to the signal, and (3) an indication of how the different time periods are represented in the graph. The graph does not need to be quantitatively accurate but should include some indication of the relevant years, in response to (3). -->

<!-- Grading Rubric -->
<!-- Axes labelled descriptively: +2 -->
<!-- Graph element corresponding to signal: +2 -->
<!-- Indication of time periods: +1 -->
<!-- Total points: X out of five -->

I drew the graph in the R software. Here is the code used for the creation, followed by the graph itself.  

```{r, fig.height=3, fig.width=7}
library(tibble)
library(ggplot2)
corrs = c(rep(0, 29), seq(0, 0.62, 0.02), seq(0.64, 0.355, -0.015))
df = tibble(years = 1940:2020, trend = corrs + 0.05, corrs = corrs + runif(81, 0, 0.1))

ggplot(data = df, aes(x = years, y = corrs)) +
  geom_line(linetype = 1) +
  geom_line(aes(y = trend), color = 'blue', linetype = 2, size = 1.5 ) +
  geom_vline(xintercept = c(1969, 2001), color = "red", linetype = 3) +
  annotate("text", x = 1969, y = 0.75, label = "Since 1969 the correlation increases.", 
           color = "darkgreen") +
  annotate("text", x = 2001, y = 0.05, label = "Since 2001 the correlation decreases.", 
           color = "darkgreen") +
  annotate("text", x = 1954, y = 0.25, label = "Indiference period\n(1940-1969)") +
  annotate("text", x = 1980, y = 0.55, label = "Differentiation period\n(1970-2000)") +
  annotate("text", x = 2010, y = 0.25, label = "Equitation period\n(2001-2020)") +
  labs(title = "Changes in average correlation between the gender of author and
the presence of selected signalling words in blurbs over the course of time",
    x = "Year of books' publication", 
    y = "Correlation between the gender of author
and the presence of signaling words",
caption = "Note: The dashed blue line indicates longitudinal trend in average correlation.
The solid black line indicates average correlation for respective year.") +
  theme_minimal()
```


# Question 2: Application

<!-- QUESTION 2: APPLICATION   Imagine you have a set of blurbs from a given time period. For each blurb, in addition to its date of appearance, you have information about whether or not the blurb comes from a newspaper (e.g., Financial Times, New York Times Book Review, Times Literary Supplement), or from an individual scholar identified solely by their academic institution (e.g., "Jonathan Lear, University of Chicago"). -->

<!-- Help your peer-reviewers: proof-read your responses, and use a level of language appropriate for an “interested member of the public” (e.g., do not use jargon and do not take a complex fact for granted). Your answers should be succinct; aim for approximately 250 words per response – or cumulatively 500 words, distributed as needed. Peer-reviewers have the authority to award zero points to a submission that exceeds a total of 1000 words. -->


## Question 2.1 -- Novelty in the set of blurbs  


<!-- QUESTION 2.1   Imagine we did an analysis similar to the French Revolution parliamentary speeches study, measuring "novelty" in this set of blurbs. Looking year by year, we find that the blurbs written by individual, academic scholars are more novel than the blurbs from newspapers. Suggest a possible explanation for how this pattern of novelty might have emerged. -->

<!-- Grading Rubric -->

<!-- Non-technical description of how novelty is measured in this set of blurbs: +2 -->

### Mesuring novelty  

We could measure novelty by finding new metaphors. More precisely, we could count how many new metaphors not used in past 5 years before blurb's publication the blurb contains.  

<!-- Specific description of a scenario that could account for higher novelty among blurbs from academic scholars compared to those from newspapers: +2 -->

### Scenario description   

The main idea is that raw reviews from academics and in newspapers are same, but a marketing department of publishing house chooses blurbs from raw reviews differently. My scenario is inspired by Simon's lecture, specifically by his citation of Rebecca L. Spang's e-mail (https://youtu.be/8rDUREWVnEM?t=808). Let's suppose for the simplicity that the newspapers' and academics' reviews contain same number of new metaphors, i.e. the raw material for blurbs is homogeneous. But then the marketing department takes its turn -- it excerpts for blurbs more often the passages with new metaphors from academics' reviews and more often the passages with old, conservative and mainstream metaphors from newspapers' reviews. The reason for the difference in blurbs is the strategic selection of the publishing house's marketing department, not the differences in raw reviews.   


<!-- Account of why/how that scenario emerged: +2 -->

### Why does the scenario emerged?  

The root of scenario is the marketing department's expectations of the public's expectations. 
<!-- The marketing department has stereotypes about what the public expects of newspapers and academia.  -->
The employees in marketing department think that the public associates universities, academia and academics with novelty, reaching new horizons, inventions, ground-breaking theories etc. That is why they preferably excerpt the novel metaphor from academic's review for the blurb, because it is coherent with novelty expectation of the public expected by marketing department. On the other hand the marketing department thinks that the public associates newspapers with mainstream, conservative, time-tested and solid ideas. That is why they preferably excerpt the old metaphors from newspaper's review, because it is coherent with the solidity expectation of the public expected by marketing department. Expectations of expectations lead to strategic selection.   

<!-- Discretionary point for creativity, interest, clarity: +1 -->
<!-- Total points: X out of 7 -->


## Question 2.2 -- Novelty and imitation across institutions    

<!-- QUESTION 2.2   Imagine we now take into account the institutional affiliation of the individual scholars writing these blurbs. Speculate on one possible pattern we might see if we measured both the novelty and the imitation for each institution and compared novelty and imitation across institutions. It may help to review the "2x2" story in Chapter 1 [59:48]. -->

<!-- Grading Rubric -->

<!-- Description of what imitation is, in relationship to novelty: +2 -->

### Description of imitation and novelty   
 
For distinguishing imitation and novelty we again use the 5 years window. The novelty we measure as a count of the metaphors not used in other blurbs in the 5 years before the publication of respective blurb. The imitation then we measure as a count of the metaphors that have been used in the 5 years before the respective blurb's publication.  

<!-- Specific description of a scenario among academic institutions that would lead to a particular imitation-versus-novelty pattern: +2 -->

### Scenario description   




<!-- Account of why/how that scenario would lead to the imitation-versus-novelty pattern described: +2 -->

### Why does the scenario lead to the imitation-versus-novelty pattern?   



<!-- Discretionary point for creativity, interest, clarity: +1 -->
<!-- Total points: X out of 7 -->









